\documentclass[12pt]{article}

% use xelatex
\title{Questions}
\author{ts6233}
\date{}

\usepackage{fontspec}
\defaultfontfeatures{Scale=MatchLowercase}
\setmainfont[Mapping=tex-text]{Minion Pro}
\setsansfont[Mapping=tex-text]{Minion Pro}
\setmonofont{Courier New}

\usepackage{xltxtra}
\usepackage{unicode-math}
\usepackage{latexsym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{lscape}

\begin{document}
\begin{enumerate}
\item In the wake of ruby (design and develop by a Japanese in 1993) and python ( design and developed by a dutch in 1991) success as scripting languages, Malaysian goverment has set-up a committe to design and build a new scripting language that would be design and build by malaysians. This new language is called \textbf{durian} ( damn good language design by malaysians ). You, as part of \textbf{durian} committee, has been asked to come up with features for this new scripting language. What are the features, and why you choose them.

\item One of the key factor for a  successful IT project is the `first to market' approach, which mean those who come up with the first original ideas or concepts have a high probability of being successful in the market. Identify `the first to market' in the current internet scenario in search engines, e-commerce, mobile application, music, e-payment, etc.

There are, however, those who are not `first to market' but rather `second to market' that have been successful. Identify these `second to market'.

Some 'second to market' even beat the `first to market'. 
What are the keys factors that influence the `second to market' success in capturing the market from `first to market'.

\item `worst is better' concept from RichardGabriel is a simple idea that a simple software that works is better than a well design software  that is complex and hard to use. Argue you case, whether you agree or not.

Give examples of `worst is better' in IT, internet and various other fields.

\item Software development in general have follow many trends or ideas. The current ideas is called agile software development or agile methodologies.

What is it and how do these approach differ from existing ideas. Do you agree with the concept?

When does it is appropriate to use agile methodologies?

\item web development frameworks are dime a dozen. What are some of the current `hot' frameworks, both in open-source and proprietry area?  Why are some of them fail to capture a significat usage, and some gain significant market share/usage?

\end{enumerate}

\end{document}
	