\documentclass[12pt]{article}
% use xelatex this
% change the font fro minion pro to someting else.
\title{Questions-2}
\author{ts6233}
\date{}

\usepackage{fontspec}
\defaultfontfeatures{Scale=MatchLowercase}
\setmainfont[Mapping=tex-text]{Minion Pro}
\setsansfont[Mapping=tex-text]{Minion Pro}
\setmonofont{Courier New}

\usepackage{xltxtra}
\usepackage{unicode-math}
\usepackage{latexsym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{lscape}

\begin{document}
\begin{enumerate}

\item Chaos theory is one of the hot research area in the 1980. What is the basis of chaos theory, and it possible application to information technology and web application. ( often, chaos theory is refered as complex system ) . What is the coonection between chaos and weather.


\item client-server technology have advanced leap and bound over the years. Some of the new technology based on client-server are cloud computing, distributed computing, parallel computing, grid computing. Describe briefly each key features of these current technology, what it key contributions/benefits. Give example where appropriate.

\item at the heart of p2p technology is the idea of sharing without a centralized server. the sharing is done equally among the peers, and this provides a big fault tolerance. Briefly, describe the p2p technology in napster, emule, gnutella, bittorent. Any possible advancement you might offer?



\item One of the widely use client-server system is e-learning. If you are asked to develop e-learning application based on open-source, what are your choice and why?

\item Briefly, what is the different between SOAP and REST? Where are these technology being used and as what? Why are they important?


\end{enumerate}

\end{document}